Search, Compress, Compile: Library Learning in Neurally-Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
better list figure
Tweaking

\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\sem}[1]{\llbracket #1 \rrbracket}

\newcommand{\system}{\textsc{SCC}~}
\newcommand{\systemEnding}{\textsc{SCC}}

\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\codechar}[1]{{\footnotesize{\texttt{"#1"}}}}

@@

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL while
  jointly training a neural network to efficiently search for programs
  in the learned DSL.  We use our model to synthesize functions on lists,
  edit text, and solve symbolic regression problems, showing how the
  model learns a domain-specific library of program components for
  expressing solutions to problems in the domain.
\end{abstract}

@@

The FlashFill system ~\cite{gulwani2011automating} developed by
Microsoft researchers and now embedded in Excel solves problems such
as these and is probably the best known practical program-induction
algorithm, but researchers in programming languages and AI have built
successful program induction algorithms for many applications, 
such as handwriting recognition and generation ~\cite{lake2015human},
procedural graphics ~\cite{ellis2017learning}, question
answering~\cite{johnson2017clevr} and robot motion
planning~\cite{devlin2017neural}, to name just a few.
These systems work in different ways, but most hinge upon having a
carefully engineered \textbf{Domain Specific Language (DSL)}.  This is
especially true for systems such as FlashFill that aim to induce a
wide range of programs very quickly, in a few seconds or less.  DSLs
constrain the search over programs with strong prior knowledge in the
form of a restricted set of programming primitives tuned to the needs
of the domain: for text editing, these are operations like appending
strings and splitting on characters.

@@

\begin{table}[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=3pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-0em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    &{\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=4pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 0\, 2]}$\to $\code{[7\, 0\, 2\, 9]}         \\
          \code{[9\, 3]}$\to $\code{[9\, 3\, 9]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ 9)}}       \\
          ~                                                  \\
          ~                                                  \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,}
      }}\\
      \hspace{1.25cm}\pop{\code{($f_0$ \codechar{.} \codechar{ }}}\\
      \hspace{1.4cm}\pop{\code{(cdr s)))}}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}&    \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}&    \pop{\code{$f($x$) = $($f_3$ x)}}\\

@@

Our \system (\textbf{(S)}search/\textbf{(C})ompress/\textbf{(C})ompile)
algorithm incorporates these insights by iterating through three steps. 
The \textbf{Search} step takes a given set of \textbf{tasks}, typically
several hundred, and searches for compact programs that solve these tasks
guided by the current DSL and neural network.
The \textbf{Compress} step grows the library (or DSL) of
domain-specific subroutines which allow the agent to more compactly
write programs in the domain; it modifies the structure of the DSL by
discovering regularities across programs found during search, compressing
them to distill out common code fragments across successful programs.
The \textbf{Compile} step improves the search procedure by training a neural network to
write programs in the current DSL, in the spirit of ``amortized'' or
``compiled'' inference~\cite{le2016inference}.%%  (CITE Goodman and Stuhlmuller,
%% and others too on amortized inference.)

>>>>

\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\sem}[1]{\llbracket{} #1 \rrbracket{}}

\newcommand{\system}{\textsc{SCC} }
\newcommand{\systemEnding}{\textsc{SCC}}

\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\codechar}[1]{{\footnotesize{\texttt{``#1''}}}}

@@

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL while
  jointly training a neural network to efficiently search for programs
  in the learned DSL.\@ We use our model to synthesize functions on lists,
  edit text, and solve symbolic regression problems, showing how the
  model learns a domain-specific library of program components for
  expressing solutions to problems in the domain.
\end{abstract}

@@

The FlashFill system~\cite{gulwani2011automating} developed by
Microsoft researchers and now embedded in Excel solves problems such
as these and is probably the best known practical program-induction
algorithm, but researchers in programming languages and AI have built
successful program induction algorithms for many applications, 
such as handwriting recognition and generation~\cite{lake2015human},
procedural graphics~\cite{ellis2017learning}, question
answering~\cite{johnson2017clevr} and robot motion
planning~\cite{devlin2017neural}, to name just a few.
These systems work in different ways, but most hinge upon having a
carefully engineered \textbf{Domain Specific Language (DSL)}.  This is
especially true for systems such as FlashFill that aim to induce a
wide range of programs very quickly, in a few seconds or less.  DSLs
constrain the search over programs with strong prior knowledge in the
form of a restricted set of programming primitives tuned to the needs
of the domain: for text editing, these are operations like appending
strings and splitting on characters.

@@

\begin{table}[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=3pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-0em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    &{\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=4pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 0\, 2]}$\to $\code{[7\, 0\, 2\, 9]}         \\
          \code{[9\, 3]}$\to $\code{[9\, 3\, 9]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ 9)}}       \\
          \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{,}
      }}\\
      \hspace{1.25cm}\pop{\code{($f_0$ \codechar{.} \codechar{ }}}\\
      \hspace{1.4cm}\pop{\code{(cdr s)))}}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}&    \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}&    \pop{\code{$f($x$) = $($f_3$ x)}}\\

@@

Our \system (\textbf{S}earch/\textbf{C}ompress/\textbf{C}ompile)
algorithm incorporates these insights by iterating through three steps. 
The \textbf{Search} step takes a given set of \textbf{tasks}, typically
several hundred, and searches for compact programs that solve these tasks
guided by the current DSL and neural network.
The \textbf{Compress} step grows the library (or DSL) of
domain-specific subroutines which allow the agent to more compactly
write programs in the domain; it modifies the structure of the DSL by
discovering regularities across programs found during search, compressing
them to distill out common code fragments across successful programs.
The \textbf{Compile} step improves the search procedure by training a neural network to
write programs in the current DSL, in the spirit of ``amortized'' or
``compiled'' inference~\cite{le2016inference}.%%  (CITE Goodman and Stuhlmuller,
%% and others too on amortized inference.)
